Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-11-28 paper/paper.tex
Consistent URL style
No need for page layout hacks
Correlation is tricky

\usepackage{placeins}

@@

For datasets, we use the same 5,725 instances used in a recent work on portfolios of algorithms for
subgraph isomorphism \citep{thelionpaper}. This collection includes randomly generated scale-free
graphs \citep{constraints10}, an assortment of real-world graphs of varying sizes \citep{LV02},
randomly generated graph pairs (using bounded degree, regular mesh, and uniform models; all are
satisfiable), segmented images~\citep{pr15,cviu11}, meshes from modelling 3D objects \citep{cviu11},
and graphs close to the satisfiable-unsatisfiable phase transition
\citep{DBLP:conf/ijcai/McCreeshPT16}. All of these instances are available in a simple text
format\footnote{\texttt{http://liris.cnrs.fr/csolnon/SIP.html}}.  Note that many of these instances
are \emph{much} larger than were used in the recent comparison of maximum common subgraph algorithms
by \citet{DBLP:conf/cp/McCreeshNPS16}: for unlabelled graphs, they used pairs of graphs with up to
35 vertices in each, whilst our dataset contains graphs with up to 6,671 vertices. For the CP
algorithm, 1,560 of the instances cannot fit in the amount of RAM we have available---we treat these
instances as having timed out. The situation for the clique encoding is even worse, and 3,653 of
these instances do not fit in 64GBytes of RAM. In contrast, for our algorithm, every instance fits
comfortably.  \section{Domain Filtering using Degrees}\label{section:degreefiltering}

@@

What about if we use instances designed for the maximum common subgraph problem? In the third plot
in \cref{figure:runtimes} we again compare these approaches, but using the first ten instances from
each family of a standard benchmark set
\citep{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}, selecting undirected, unlabelled
graphs with up to 50 vertices---this gives us a total of 4,110 instances. In these instances the
number of vertices in the pattern and target graphs is the same, which is not ideal for our
algorithm (although our invariants are still effective in many cases). Nonetheless, we are by a
small margin the single strongest solver. Interestingly, our algorithm tends to have complementary
performance to the other two approaches (which are much more correlated), which suggests that there
is scope for an algorithm which runs both an upper bound and a constructive, lower bound approach
simultaneously or in parallel, stopping when the two bounds meet in the middle.

@@

\FloatBarrier
\clearpage

>>>>

@@

For datasets, we use the same 5,725 instances used in a recent work on portfolios of algorithms for
subgraph isomorphism \citep{thelionpaper}. This collection includes randomly generated scale-free
graphs \citep{constraints10}, an assortment of real-world graphs of varying sizes \citep{LV02},
randomly generated graph pairs (using bounded degree, regular mesh, and uniform models; all are
satisfiable), segmented images~\citep{pr15,cviu11}, meshes from modelling 3D objects \citep{cviu11},
and graphs close to the satisfiable-unsatisfiable phase transition
\citep{DBLP:conf/ijcai/McCreeshPT16}. All of these instances are available in a simple text
format\footnote{http://liris.cnrs.fr/csolnon/SIP.html}.  Note that many of these instances
are \emph{much} larger than were used in the recent comparison of maximum common subgraph algorithms
by \citet{DBLP:conf/cp/McCreeshNPS16}: for unlabelled graphs, they used pairs of graphs with up to
35 vertices in each, whilst our dataset contains graphs with up to 6,671 vertices. For the CP
algorithm, 1,560 of the instances cannot fit in the amount of RAM we have available---we treat these
instances as having timed out. The situation for the clique encoding is even worse, and 3,653 of
these instances do not fit in 64GBytes of RAM. In contrast, for our algorithm, every instance fits
comfortably.  \section{Domain Filtering using Degrees}\label{section:degreefiltering}

@@

What about if we use instances designed for the maximum common subgraph problem? In the third plot
in \cref{figure:runtimes} we again compare these approaches, but using the first ten instances from
each family of a standard benchmark set
\citep{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}, selecting undirected, unlabelled
graphs with up to 50 vertices---this gives us a total of 4,110 instances. In these instances the
number of vertices in the pattern and target graphs is the same, which is not ideal for our
algorithm (although our invariants are still effective in many cases). Nonetheless, we are by a
small margin the single strongest solver. Interestingly, our algorithm tends to have complementary
performance to the clique approach, which suggests that there is scope for an algorithm which runs
both an upper bound and a constructive, lower bound approach simultaneously or in parallel, stopping
when the two bounds meet in the middle.

@@
